### 2018-05-02 doc/paper.tex
Adding commands for the "partial b" terms.
Also

- Adding subsections to the K-compensated section
- Dropping some unnecessary parentheses
- Changing some terms in the proof sketch of the error
  bound

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\qed}{\(\blacksquare\)}
\newcommand{\cond}[1]{\operatorname{cond}\left(#1\right)}
\newcommand{\fl}[1]{\operatorname{fl}\left(#1\right)}
\newcommand{\eps}{\varepsilon}
\newcommand{\mach}{\mathbf{u}}

@@

\begin{enumerate}
  \item If \(\delta_i \leq \mach\), \(\rho_i = \pm 1\), then
      \(\prod_{i = 1}^n (1 + \delta_i)^{\rho_i} = 1 + \theta_n\),
  \item \(\left|\theta_n\right| \leq \gamma_n \coloneqq
      n \mach / (1 - n \mach)\),
  \item \((1 + \theta_k)(1 + \theta_j) \leq (1 + \theta_{k + j})\),
  \item \(\gamma_k + \gamma_j + \gamma_k \gamma_j \leq \gamma_{k + j}\),
  \item \((1 + \mach)^j \leq 1 / (1 - j \mach)\).
\end{enumerate}

@@

\noindent By defining the global errors at each step
\begin{equation}
  \partial b_j^{(k)} = b_j^{(k)} - \widehat{b}_j^{(k)}
\end{equation}
we can see (Figure~\ref{fig:loc-err-accumulate}) that the local errors
accumulate in
\(\partial b^{(k)}\):
\begin{equation}\label{err-update}
  \partial b_j^{(k)} = (1 - s) \cdot \partial b_j^{(k + 1)} + s \cdot
  \partial b_{j + 1}^{(k + 1)} + \ell_{1, j}^{(k)}.
\end{equation}
When computed in exact arithmetic, we would have
\begin{equation}
  p(s) = \widehat{b}_0^{(0)} + \partial b_0^{(0)}
\end{equation}
and by using \eqref{err-update}, we can continue to compute
approximations of \(\partial b_j^{(k)}\). The idea behind the compensated
de Casteljau algorithm is to compute both the local error and the updates
of the global error with floating point operations:

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$b, s$}
      \State \(n = \texttt{length}(b) - 1\)
      \State \(\left[\widehat{r}, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(\widehat{b}_j^{(n)} = b_j\)
        \State \(\widehat{\partial b}_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              \widehat{r}, \widehat{b}_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, \widehat{b}_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[\widehat{b}_j^{(k)}, \sigma_3\right] =
              \mathtt{TwoSum}(P_1, P_2)\)
          \State \(\widehat{\ell}_{1, j}^{(k)} = \pi_1 \oplus \pi_2 \oplus
              \sigma_3 \oplus \left(\rho \otimes
              \widehat{b}_j^{(k + 1)}\right)\)
          \State \(\widehat{\partial b}_j^{(k)} =
              \left(\widehat{r} \otimes
              \widehat{\partial b}_j^{(k + 1)}\right) \oplus
              \left(s \otimes \widehat{\partial b}_{j + 1}^{(k + 1)}
              \right) \oplus
              \widehat{\ell}_{1, j}^{(k)}\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = \widehat{b}_0^{(0)} \oplus
          \widehat{\partial b}_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

@@

\begin{theorem}[\cite{Jiang2010}]
  If no underflow occurs and \(n \geq 2\), then
  \begin{equation}
    \left|\partial b_0^{(0)} - \widehat{\partial b}_0^{(0)}\right| \leq
    2 \gamma_{3n + 1} \gamma_{3(n - 1)}
    \sum_{j = 0}^n \left|b_j\right| B_{j, n}(s).
  \end{equation}
\end{theorem}

\noindent Using the bound on the error in \(\partial b\), the algorithm can
be shown to be as accurate as if the computations were done in twice
the working precision:

@@

Unfortunately, Figure~\ref{fig:compensated-insufficient} shows how
the \texttt{CompDeCasteljau} starts to break down in a region of
high condition number (caused by a multiple root with multiplicity
higher than two). For example, the point
\(s = \frac{1}{2} + 1001\mach\)
--- which is in the plotted region \(\left|s - \frac{1}{2}\right|
\leq 1.5 \cdot 10^{-11}\) --- evaluates to exactly \(0\) when it should be
\(\mathcal{O}\left(\mach^3\right)\). As shown in
Table~\ref{tab:exact-computation}, the breakdown occurs because
\(\widehat{b}_0^{(0)} = -\widehat{\partial b}_0^{(0)} = \mach / 16\).

\begin{table}
  \centering
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & \widehat{b}_j^{(k)} & \widehat{\partial b}_j^{(k)} & \partial b_j^{(k)} - \widehat{\partial b}_j^{(k)} \\
    \midrule
    3 & 0 & 0.125 - 1.75 (1001 \mach) - 0.25 \mach & 0.25\mach & 0 \\
    3 & 1 & -0.125 + 1.25(1001 \mach) + 0.25 \mach & -0.25\mach & 0 \\
    3 & 2 & 0.125 - 0.75 (1001 \mach) & 0 & 0 \\
    3 & 3 & -0.125 + 0.25 (1001 \mach) & 0 & 0 \\
    \midrule
    2 & 0 & -0.5 (1001 \mach) & 3 (1001 \mach)^2 & 0 \\
    2 & 1 & 0.5(1001 \mach) + 0.125 \mach & -0.125\mach - 2 (1001 \mach)^2 & 0 \\
    2 & 2 & -0.5 (1001 \mach) & (1001 \mach)^2 & 0 \\
    \midrule
    1 & 0 & 0.0625\mach + (1001 \mach)^2 + 239\mach^2 & -0.0625\mach + 0.5  (1001 \mach)^2 - 239 \mach^2 & -5 (1001\mach)^3 \\
    1 & 1 & 0.0625\mach - (1001 \mach)^2 - 239\mach^2 & -0.0625\mach - 0.5  (1001 \mach)^2 + 239 \mach^2 & 3 (1001\mach)^3 \\
    \midrule
    0 & 0 & 0.0625 \mach & -0.0625 \mach & -4 (1001 \mach)^3 + 8 (1001 \mach)^4 \\
    \bottomrule
  \end{tabular}
  \captionsetup{width=.75\linewidth}
  \caption{Terms computed by \texttt{CompDeCasteljau} when evaluating \\
    \(p(s) = (2s - 1)^3 (s - 1)\) at the point
    \(s = \frac{1}{2} + 1001 \mach\)}
  \label{tab:exact-computation}
\end{table}

@@

In order to raise from twice the working precision to \(K\) times the
working precision, we continue using EFTs when computing
\(\widehat{\partial b}^{(k)}\). By tracking the round-off from each
floating point evaluation via an EFT, we can form a cascade of global errors:
\begin{align}
  b_j^{(k)} &= \widehat{b}_j^{(k)} + \partial b_j^{(k)} \\
  \partial b_j^{(k)} &= \widehat{\partial b}_j^{(k)} + \partial^2 b_j^{(k)} \\
  \partial^2 b_j^{(k)} &= \widehat{\partial^2 b}_j^{(k)} +
  \partial^3 b_j^{(k)} \\
  & \vdots \nonumber
\end{align}
In the same way local error can be tracked when updating
\(\widehat{b}_j^{(k)}\), it can be tracked for updates that happen down
the cascade:
\begin{alignat}{4}
  (1 - s) \cdot \widehat{b}_j^{(k + 1)} &+
  s \cdot \widehat{b}_{j + 1}^{(k + 1)} &&  &&=
  \widehat{b}_j^{(k)} &&+ \ell_{1, j}^{(k)} \\
  (1 - s) \cdot \widehat{\partial b}_j^{(k + 1)} &+
  s \cdot \widehat{\partial b}_{j + 1}^{(k + 1)} &&+ \ell_{1, j}^{(k)} &&=
  \widehat{\partial b}_j^{(k)} &&+ \ell_{2, j}^{(k)} \\
  (1 - s) \cdot \widehat{\partial^2 b}_j^{(k + 1)} &+
  s \cdot \widehat{\partial^2 b}_{j + 1}^{(k + 1)} &&+ \ell_{2, j}^{(k)} &&=
  \widehat{\partial^2 b}_j^{(k)} &&+ \ell_{3, j}^{(k)} \\
  &  &&  &&\vdots && \nonumber
\end{alignat}

\begin{figure}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\widehat{\partial b}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\widehat{\partial^2 b}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\widehat{\partial^3 b}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\widehat{\partial b}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\widehat{\partial^2 b}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\widehat{\partial^3 b}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\widehat{\partial b}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\widehat{\partial^2 b}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\widehat{\partial^3 b}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Filtering errors}
\label{fig:error-filtration}
\end{figure}

In \texttt{CompDeCasteljau} (Algorithm~\ref{alg:comp-de-casteljau}), after
a single stage of error filtering we
``give up'' and use \(\widehat{\partial b}\) instead of
\(\partial b\) (without keeping around any information about the
round-off error). In order to obtain results that are as accurate as if
computed in \(K\) times the working precision, we must continue filtering
(see Figure~\ref{fig:error-filtration})
errors down \((K - 1)\) times, and only at the final level do we accept
the rounded
\(\widehat{\partial^{K - 1} b}\) in place of the exact
\(\partial^{K - 1} b\).

When computing \(\widehat{\partial^F b}\) (i.e. the error after
\(F\) stages of filtering)
there will be several sources of round-off. In particular, there will be
\begin{itemize}
\item errors when computing \(\widehat{\ell}_{F, j}^{(k)}\) from the
  terms in \(\ell_{F, j}^{(k)}\)
\item an error
for the ``missing'' \(\rho \cdot \widehat{\partial^F b}_j^{(k + 1)}\) in
\((1 - s) \cdot \widehat{\partial^F b}_j^{(k + 1)}\)
\item an error from the product
  \(\widehat{r} \otimes \widehat{\partial^F b}_j^{(k + 1)}\)
\item an error from the product
  \(s \otimes \widehat{\partial^F b}_{j + 1}^{(k + 1)}\)
\item two errors from the two \(\oplus\) when combining the three
  terms in
  \(\left[\widehat{r} \otimes \widehat{\partial^F b}_j^{(k + 1)}\right] \oplus
  \left[s \otimes \widehat{\partial^F b}_{j + 1}^{(k + 1)}\right] \oplus
  \widehat{\ell}_{F, j}^{(k)}\)
\end{itemize}
For example, in~\eqref{ell-j}:
%% H/T: https://tex.stackexchange.com/a/154333/32270
\begin{equation}
\ell_{1, j}^{(k)} =
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_1}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 = \widehat{r} \otimes \widehat{b}_j^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_2}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_2 = s \otimes \widehat{b}_{j + 1}^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \sigma_3}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 \oplus P_2} +
    \underbrace{\rho \cdot \widehat{b}_j^{(k + 1)}}_{
        (1 - s) \widehat{b}_j^{(k + 1)}}
\end{equation}
After each stage, we'll always have
\begin{equation}
\ell_{F, j}^{(k)} = e_1 + e_2 + \cdots + e_M + \rho \cdot
\widehat{\partial^{F - 1} b}_j^{(k + 1)}
\end{equation}
where the terms \(e_1, \ldots, e_M\) come from using \texttt{TwoSum} and
\texttt{TwoProd} when computing \(\widehat{\partial^{F - 1} b}_j^{(k)}\)
and the \(\rho\) term comes from the roundoff
in \(1 \ominus s\) when multiplying \((1 - s)\) by
\(\widehat{\partial^{F - 1} b}_j^{(k + 1)}\). With this in mind, we
can define an EFT (\texttt{LocalErrorEFT}) that computes
\(\widehat{\ell}\) and tracks all round-off errors generated in
the process:

@@

>>>>

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\qed}{\(\blacksquare\)}
\newcommand{\cond}[1]{\operatorname{cond}\left(#1\right)}
\newcommand{\fl}[1]{\operatorname{fl}\left(#1\right)}
\newcommand{\eps}{\varepsilon}
\newcommand{\mach}{\mathbf{u}}
%% db == ``delta'' b
\newcommand{\db}[1]{
  \ifthenelse{\equal{#1}{1}}
             {\partial b}
             {\partial^{#1} b}
}
%% cdb == computed ``delta'' b
\newcommand{\cdb}[1]{
  \ifthenelse{\equal{#1}{1}}
             {\widehat{\partial b}}
             {\widehat{\partial^{#1} b}}
}

@@

\begin{enumerate}
  \item If \(\delta_i \leq \mach\), \(\rho_i = \pm 1\), then
      \(\prod_{i = 1}^n (1 + \delta_i)^{\rho_i} = 1 + \theta_n\),
  \item \(\left|\theta_n\right| \leq \gamma_n \coloneqq
      n \mach / (1 - n \mach)\),
  \item \((1 + \theta_k)(1 + \theta_j) \leq 1 + \theta_{k + j}\),
  \item \(\gamma_k + \gamma_j + \gamma_k \gamma_j \leq \gamma_{k + j}\),
  \item \((1 + \mach)^j \leq 1 / (1 - j \mach)\).
\end{enumerate}

@@

\noindent By defining the global errors at each step
\begin{equation}
  \db{1}_j^{(k)} = b_j^{(k)} - \widehat{b}_j^{(k)}
\end{equation}
we can see (Figure~\ref{fig:loc-err-accumulate}) that the local errors
accumulate in
\(\db{1}^{(k)}\):
\begin{equation}\label{err-update}
  \db{1}_j^{(k)} = (1 - s) \cdot \db{1}_j^{(k + 1)} + s \cdot
  \db{1}_{j + 1}^{(k + 1)} + \ell_{1, j}^{(k)}.
\end{equation}
When computed in exact arithmetic, we would have
\begin{equation}
  p(s) = \widehat{b}_0^{(0)} + \db{1}_0^{(0)}
\end{equation}
and by using \eqref{err-update}, we can continue to compute
approximations of \(\db{1}_j^{(k)}\). The idea behind the compensated
de Casteljau algorithm is to compute both the local error and the updates
of the global error with floating point operations:

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$b, s$}
      \State \(n = \texttt{length}(b) - 1\)
      \State \(\left[\widehat{r}, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(\widehat{b}_j^{(n)} = b_j\)
        \State \(\cdb{1}_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              \widehat{r}, \widehat{b}_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, \widehat{b}_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[\widehat{b}_j^{(k)}, \sigma_3\right] =
              \mathtt{TwoSum}(P_1, P_2)\)
          \State \(\widehat{\ell}_{1, j}^{(k)} = \pi_1 \oplus \pi_2 \oplus
              \sigma_3 \oplus \left(\rho \otimes
              \widehat{b}_j^{(k + 1)}\right)\)
          \State \(\cdb{1}_j^{(k)} =
              \left(\widehat{r} \otimes
              \cdb{1}_j^{(k + 1)}\right) \oplus
              \left(s \otimes \cdb{1}_{j + 1}^{(k + 1)}
              \right) \oplus
              \widehat{\ell}_{1, j}^{(k)}\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = \widehat{b}_0^{(0)} \oplus
          \cdb{1}_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

@@

\begin{theorem}[\cite{Jiang2010}]
  If no underflow occurs and \(n \geq 2\), then
  \begin{equation}
    \left|\db{1}_0^{(0)} - \cdb{1}_0^{(0)}\right| \leq
    2 \gamma_{3n + 1} \gamma_{3(n - 1)}
    \sum_{j = 0}^n \left|b_j\right| B_{j, n}(s) =
    2 \gamma_{3n + 1} \gamma_{3(n - 1)} \widetilde{p}(s).
  \end{equation}
\end{theorem}

\noindent Using the bound on the error in \(\db{1}\), the algorithm can
be shown to be as accurate as if the computations were done in twice
the working precision:

@@

Unfortunately, Figure~\ref{fig:compensated-insufficient} shows how
the \texttt{CompDeCasteljau} starts to break down in a region of
high condition number (caused by a multiple root with multiplicity
higher than two). For example, the point
\(s = \frac{1}{2} + 1001\mach\)
--- which is in the plotted region \(\left|s - \frac{1}{2}\right|
\leq 1.5 \cdot 10^{-11}\) --- evaluates to exactly \(0\) when it should be
\(\mathcal{O}\left(\mach^3\right)\). As shown in
Table~\ref{tab:exact-computation}, the breakdown occurs because
\(\widehat{b}_0^{(0)} = -\cdb{1}_0^{(0)} = \mach / 16\).

\begin{table}
  \centering
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & \widehat{b}_j^{(k)} & \cdb{1}_j^{(k)} & \db{1}_j^{(k)} - \cdb{1}_j^{(k)} \\
    \midrule
    3 & 0 & 0.125 - 1.75 (1001 \mach) - 0.25 \mach & 0.25\mach & 0 \\
    3 & 1 & -0.125 + 1.25(1001 \mach) + 0.25 \mach & -0.25\mach & 0 \\
    3 & 2 & 0.125 - 0.75 (1001 \mach) & 0 & 0 \\
    3 & 3 & -0.125 + 0.25 (1001 \mach) & 0 & 0 \\
    \midrule
    2 & 0 & -0.5 (1001 \mach) & 3 (1001 \mach)^2 & 0 \\
    2 & 1 & 0.5(1001 \mach) + 0.125 \mach & -0.125\mach - 2 (1001 \mach)^2 & 0 \\
    2 & 2 & -0.5 (1001 \mach) & (1001 \mach)^2 & 0 \\
    \midrule
    1 & 0 & 0.0625\mach + (1001 \mach)^2 + 239\mach^2 & -0.0625\mach + 0.5  (1001 \mach)^2 - 239 \mach^2 & -5 (1001\mach)^3 \\
    1 & 1 & 0.0625\mach - (1001 \mach)^2 - 239\mach^2 & -0.0625\mach - 0.5  (1001 \mach)^2 + 239 \mach^2 & 3 (1001\mach)^3 \\
    \midrule
    0 & 0 & 0.0625 \mach & -0.0625 \mach & -4 (1001 \mach)^3 + 8 (1001 \mach)^4 \\
    \bottomrule
  \end{tabular}
  \captionsetup{width=.75\linewidth}
  \caption{Terms computed by \texttt{CompDeCasteljau} when evaluating \\
    \(p(s) = (2s - 1)^3 (s - 1)\) at the point
    \(s = \frac{1}{2} + 1001 \mach\)}
  \label{tab:exact-computation}
\end{table}

@@

\subsection{Algorithm Specified}

In order to raise from twice the working precision to \(K\) times the
working precision, we continue using EFTs when computing
\(\cdb{1}^{(k)}\). By tracking the round-off from each
floating point evaluation via an EFT, we can form a cascade of global errors:
\begin{align}
  b_j^{(k)} &= \widehat{b}_j^{(k)} + \db{1}_j^{(k)} \\
  \db{1}_j^{(k)} &= \cdb{1}_j^{(k)} + \db{2}_j^{(k)} \\
  \db{2}_j^{(k)} &= \cdb{2}_j^{(k)} +
  \db{3}_j^{(k)} \\
  & \vdots \nonumber
\end{align}
In the same way local error can be tracked when updating
\(\widehat{b}_j^{(k)}\), it can be tracked for updates that happen down
the cascade:
\begin{alignat}{4}
  (1 - s) \cdot \widehat{b}_j^{(k + 1)} &+
  s \cdot \widehat{b}_{j + 1}^{(k + 1)} &&  &&=
  \widehat{b}_j^{(k)} &&+ \ell_{1, j}^{(k)} \\
  (1 - s) \cdot \cdb{1}_j^{(k + 1)} &+
  s \cdot \cdb{1}_{j + 1}^{(k + 1)} &&+ \ell_{1, j}^{(k)} &&=
  \cdb{1}_j^{(k)} &&+ \ell_{2, j}^{(k)} \\
  (1 - s) \cdot \cdb{2}_j^{(k + 1)} &+
  s \cdot \cdb{2}_{j + 1}^{(k + 1)} &&+ \ell_{2, j}^{(k)} &&=
  \cdb{2}_j^{(k)} &&+ \ell_{3, j}^{(k)} \\
  &  &&  &&\vdots && \nonumber
\end{alignat}

\begin{figure}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\cdb{1}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\cdb{2}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\cdb{3}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\cdb{1}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\cdb{2}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\cdb{3}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\cdb{1}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\cdb{2}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\cdb{3}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Filtering errors}
\label{fig:error-filtration}
\end{figure}

In \texttt{CompDeCasteljau} (Algorithm~\ref{alg:comp-de-casteljau}), after
a single stage of error filtering we
``give up'' and use \(\cdb{1}\) instead of
\(\db{1}\) (without keeping around any information about the
round-off error). In order to obtain results that are as accurate as if
computed in \(K\) times the working precision, we must continue filtering
(see Figure~\ref{fig:error-filtration})
errors down \((K - 1)\) times, and only at the final level do we accept
the rounded
\(\cdb{K - 1}\) in place of the exact
\(\db{K - 1}\).

When computing \(\cdb{F}\) (i.e. the error after
\(F\) stages of filtering)
there will be several sources of round-off. In particular, there will be
\begin{itemize}
\item errors when computing \(\widehat{\ell}_{F, j}^{(k)}\) from the
  terms in \(\ell_{F, j}^{(k)}\)
\item an error
for the ``missing'' \(\rho \cdot \cdb{F}_j^{(k + 1)}\) in
\((1 - s) \cdot \cdb{F}_j^{(k + 1)}\)
\item an error from the product
  \(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\)
\item an error from the product
  \(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\)
\item two errors from the two \(\oplus\) when combining the three
  terms in
  \(\left[\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right] \oplus
  \left[s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right] \oplus
  \widehat{\ell}_{F, j}^{(k)}\)
\end{itemize}
For example, in~\eqref{ell-j}:
%% H/T: https://tex.stackexchange.com/a/154333/32270
\begin{equation}
\ell_{1, j}^{(k)} =
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_1}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 = \widehat{r} \otimes \widehat{b}_j^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_2}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_2 = s \otimes \widehat{b}_{j + 1}^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \sigma_3}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 \oplus P_2} +
    \underbrace{\rho \cdot \widehat{b}_j^{(k + 1)}}_{
        (1 - s) \widehat{b}_j^{(k + 1)}}
\end{equation}
After each stage, we'll always have
\begin{equation}
\ell_{F, j}^{(k)} = e_1 + e_2 + \cdots + e_M + \rho \cdot
\cdb{F - 1}_j^{(k + 1)}
\end{equation}
where the terms \(e_1, \ldots, e_M\) come from using \texttt{TwoSum} and
\texttt{TwoProd} when computing \(\cdb{F - 1}_j^{(k)}\)
and the \(\rho\) term comes from the roundoff
in \(1 \ominus s\) when multiplying \((1 - s)\) by
\(\cdb{F - 1}_j^{(k + 1)}\). With this in mind, we
can define an EFT (\texttt{LocalErrorEFT}) that computes
\(\widehat{\ell}\) and tracks all round-off errors generated in
the process:

@@

\subsection{Error bound for polynomial evaluation}
